\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories

### 2023-11-15 paper.tex
modifi unsavedchanges for merge

To address the feasibility and performance trade-offs of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams (as shown in \Cref{fig:cross-traj-comparison-set})
These \emph{cross-trajectory co-observations} allow sub-teams to obtain trajectories that are closer to the optimal (as shown in Figure \ref{fig:cross-traj-comparison-set}), because they do not require the entire \emph{sub-team} to meet with other teams for co-observations, thus providing more flexibility. Technically, \rtron{we can always create a trivial schedule that involves only co-observations between members of the same team; this, however, would make the solution more vulnerable in the case where multiple agents are compromised in the same team. While in this paper we explicitly consider only the single attacker scenario, multi-attacks can be potentially handled by taking advantage of the \emph{decentralized blocklist protocol} introduced in \cite{wardega2023byzantine}. For this reason, we setup the methods presented below to always prefer \emph{cross-trajectory co-observation} when feasible.}\rtron{Probably move this later.}

>>>>

To address the feasibility and performance trade-offs of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams (as shown in \Cref{fig:cross-traj-comparison-set})
These \emph{cross-trajectory co-observations} allow sub-teams to obtain trajectories that are closer to the optimal (as shown in Figure \ref{fig:cross-traj-comparison-set}), because they do not require the entire \emph{sub-team} to meet with other teams for co-observations, thus providing more flexibility. Technically, \rtron{we can always create a trivial schedule that involves only co-observations between members of the same team; this, however, would make the solution more vulnerable in the case where multiple agents are compromised in the same team. While in this paper we explicitly consider only the single attacker scenario, multi-attacks can be potentially handled by taking advantage of the \emph{decentralized blocklist protocol} introduced in \cite{wardega2023byzantine}. For this reason, we setup the methods presented below to always prefer \emph{cross-trajectory co-observation} when feasible.}\rtron{Probably move this later.  }
